Pillar 2 - Topic Modeling

### 2019-03-12 Pillar 2 - Topic Modeling.Rmd
integrates Topic Scores code

```{r saving models, eval= TRUE}
save(topic_model,
     file = "Output/topic_model.RDATA")

@@

```{r LDA fitxxxxxxx, cache = TRUE}
n_topics <- c(35, 35, 40)
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

>>>>

```{r getting gamma and beta, eval = TRUE}
get_beta <- function(results){

  tidy(results, matrix = "beta")           %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(beta) )

get_gamma <- function(results){

  tidy(results, matrix = "gamma")          %>%
    mutate(topic = paste("Topic", topic) ) %>%
      arrange(topic, desc(gamma) )
}

```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```
#Saving DELETE LATER
```{r saving tidy models, eval= TRUE}
save(topic_model_gb,
     file = "Output/topic_model_gb.RDATA")

save(topic_model_gb,
     file = "App/Recommender System/topic_model_gb.RDATA")
```
#Saving DELETE LATER
```{r saving models, eval= TRUE}
save(topic_model,
     file = "Output/topic_model.RDATA")

@@

##Distributions of best models
```{r Distributions, eval = TRUE}
#select number of topics
n_topics_overview <- 36
n_topics_manual   <- 40

#Crop models
TM_overview <- topic_model_gb %>%
  filter(n_topic== n_topics_overview)

TM_manual   <- topic_model_gb %>%
  filter(n_topic== n_topics_manual)

#Distributions
distribution <- list()

distribution$beta$overview  <- TM_overview %>% pull(b_overview)
distribution$beta$manual    <- TM_manual   %>% pull(b_manual)

distribution$gamma$overview <- TM_overview %>% pull(g_overview)
distribution$gamma$manual   <- TM_manual   %>% pull(g_manual)

```
##Inspect topics
THE TOPICS ARE SUPPER STRANGE!
```{r inspect topics, eval = T}

inspect_topics <- function(d_beta){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(10, beta)

topics <-  lapply(
  distribution$beta,
  inspect_topics
)
```
##Selectig keywords
```{r key words, eval = TRUE}
get_top_words <- function(d_beta, n = 3){
  data.frame(d_beta) %>%
    group_by(topic) %>%
    top_n(n, beta) %>%
    pull(term)%>%
    unique
}

kw <- lapply(
  distribution$beta,
  get_top_words
)
```
##Convenience vectors for APP
```{r for convenience, eval = T}
# set seed
set.seed(1)

#
## All courses
course_all <- d_course %>%
  inner_join(
    d_transcript,
    by = "Course ID"
  ) %>%
  distinct(
    `Course ID`
  ) %>%
  # remove semester abroad, skills and projects
  filter(
    ! str_detect(`Course ID`, pattern = "SA|SKI|PRO")
  ) %>%
  pull

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```
###Previous code DELETE LATER
```{r LDA fitxxxxxxx, cache = TRUE}
n_topics <- c(35, 35, 40)
levels   <- c("description", "overview", "manual")
list_nam <- character(0)
